Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
updates

In serial, we have:

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) & Speedup \\ \hline
%(128, 128) & 2 & 2 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 4 & 2 & (still queued on Odyssey) & \\ \hline %check
%(128, 128) & 4 & 4 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 8 & 8 & (still queued on Odyssey) & \\ \hline
(256, 256) & 2 & 2 & 2.57 & 3.07\\ \hline %real
(256, 256) & 4 & 2 & 11.32 & \\ \hline %check
(256, 256) & 4 & 4 & 13.65 & \\ \hline %check
(256, 256) & 8 & 8 & (still queued on Odyssey)& \\ \hline %check17.44
(512, 512) & 2 & 2 & 39.65 & 1.61\\ \hline %real
(512, 512) & 4 & 2 & 14.46 & 4.42\\ \hline
(512, 512) & 4 & 4 & (still queued on Odyssey)&\\ \hline %check
(512, 512) & 8 & 8 & (still queued on Odyssey)&\\ \hline %check
\end{tabular}
\end{center}

Note that as the workload assigned to each processing element stays constant and more processors are used to solve a larger problem, near-linear scaling is achieved. However, scaling is \textbf{not} achieved when we simply add more processing elements to try to solve the same-sized problem, as there is greater constant startup costs which do not necessarily improve the speed (or perhaps even decrease speed). Hence, this is an example of weak scaling. However, an advantage to this paradigm is that because each processor only communicates with its nearest neighbors, communication overhead is relatively constant regardless of how large problem size / number of processors used becomes. Therefore, such a paradigm should scale well to larger problem sizes or more fine grid spacings.

\subsection{Summary of Performance}

TODO team

\subsection{Demonstrating Scaling and Efficiency}

\subsection{Parallel in Space}

bsim TODO eventually

As we can see, we do see the effects of WEAK scaling

TODO analyze

>>>>

\subsection{Summary of Performance}
\subsubsection{Parallel in Space Paradigm}
In serial, we have:

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|} \hline
($N_x, N_y$) & $P_x$ & $P_y$ & Time (sec) & Speedup \\ \hline
%(128, 128) & 2 & 2 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 4 & 2 & (still queued on Odyssey) & \\ \hline %check
%(128, 128) & 4 & 4 & (still queued on Odyssey) & \\ \hline
%(128, 128) & 8 & 8 & (still queued on Odyssey) & \\ \hline
(256, 256) & 2 & 2 & 2.57 & 3.07\\ \hline %real
(256, 256) & 4 & 2 & 11.32 & 0.70\\ \hline %check
(256, 256) & 4 & 4 & (still queued on Odyssey) & \\ \hline %check 13.65
(256, 256) & 8 & 8 & (still queued on Odyssey)& \\ \hline %check 17.44
(512, 512) & 2 & 2 & 39.65 & 1.61\\ \hline %real
(512, 512) & 4 & 2 & 14.46 & 4.42\\ \hline %real
(512, 512) & 4 & 4 & 8.02 & 7.97\\ \hline 
(512, 512) & 8 & 8 & (still queued on Odyssey)&\\ \hline 
\end{tabular}
\end{center}

\subsection{Demonstrating Scaling and Efficiency}
\subsubsection{Parallel in Space Paradigm}
Note that as the workload assigned to each processing element stays constant and more processors are used to solve a larger problem, near-linear scaling is achieved. However, scaling is \textbf{not} achieved for the 256$\times$ 256 grid when we simply add more processing elements to try to solve the same-sized problem, as there is greater constant startup costs which do not necessarily improve the speed (or perhaps even decrease speed). We do see scaling with approximately $50\%$ efficiency for the $512\times 512$ grid as we add more processors. From the results, as we go from the $256\times256$ grid to the $512\times 512$ grid, we quadruple the size of the problem; quadrupling the processors from $2\times 2$ to $4\times4$ yields a somewhat linear relationship. Hence, this is an example of weak scaling. An advantage to this paradigm is as follows: because each processor only communicates with its nearest neighbors, communication overhead is relatively constant regardless of how large problem size / number of processors used becomes. Therefore, such a paradigm should scale well to larger problem sizes or more fine grid spacings.
